Automatic Identification and Annotation of Parallel Tasks in Structured Programs

### 2018-01-08 docs/ACM/paper.tex
Adding some of Guido's remarks to the paper.

The use of OpenMP pragmas as the concrete means to explore, without human
intervention, task parallelism in programs presents difficulties and
advantages. 
Such challenges and benefits have guided the design and implementation of the
techniques \rmv{that we discuss} \new{described in} ection~\ref{sec:sol}.
\guido{The techniques or the advantages/difficulties? Ambiguous.} 
In the rest of this section \ed{we discuss such advantage and difficulties.}

@@

\guido{The runtime is a consequence; the main advantage is the possibility of leaving to a
runtime the task of handling dependences dynamically.} 
The main advantage of using OpenMP \new{annotations} to split a program into parallel tasks is
\new{the ability  of leaving the job of  handling dependences to a runtime.}
\new{The OpenMP runtime maintains a task dependence graph which dynamically exposes more parallelism 
opportunities than those resulting from a conservative  compile-time  analysis.}
\new{In particular, the} runtime lets us circumvent the shortcomings that pointer aliasing
impose on the automatic parallelization of code.
Aliasing -- the possibility of two pointers dereferencing the same
memory region -- either prevents parallelism altogether, or forces compilers to
resort to complex runtime checks to ensure its correctness~\cite{Alves15,Rus02}.
The OpenMP runtime shields us from this problem, because
it already checks for dependencies among tasks, and dispatches them in a
correct order~\cite{LaGrone11}. \ed{To achieve that, OpenMP runtime uses task descriptors that contain}
\guido{The descriptor does not keep task status; this is done in the runtime.}
\rmv{task's status (running, waiting)} \ed{a task identifier and  a list of memory addresses corresponding to the task input /output arguments.}

>>>>

The use of OpenMP pragmas as the concrete means to explore, without human
intervention, task parallelism in programs presents difficulties and
advantages. 
Such challenges and benefits have guided the design and implementation of the
techniques described in Section~\ref{sec:sol}.
In the rest of this section we discuss such advantage and difficulties.

@@

The main advantage of using OpenMP annotations to split a program into parallel
tasks is
the ability  of leaving the job of  handling dependences to a runtime.
The OpenMP runtime maintains a task dependence graph which dynamically exposes more parallelism 
opportunities than those resulting from a conservative  compile-time  analysis.
In particular, the runtime lets us circumvent the shortcomings that pointer aliasing
impose on the automatic parallelization of code.
Aliasing -- the possibility of two pointers dereferencing the same
memory region -- either prevents parallelism altogether, or forces compilers to
resort to complex runtime checks to ensure its correctness~\cite{Alves15,Rus02}.
The OpenMP runtime shields us from this problem, because
it already checks for dependencies among tasks, and dispatches them in a
correct order~\cite{LaGrone11}. \ed{To achieve that, OpenMP runtime uses task descriptors that contain}
\guido{The descriptor does not keep task status; this is done in the runtime.}
\rmv{task's status (running, waiting)} \ed{a task identifier and  a list of memory addresses corresponding to the task input /output arguments.}
